The Community Land Model, version 5.1 \\ One-at-a-time Parameter Perturbation Ensemble

### 2024-04-04 ms/ms.tex

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{../figs/variance.pdf}
\caption{Cumulative fraction of variance explained by the most influential parameters on gross primary production and canopy evaporation. For example, approximately 96\% of canopy evaporation variance is explained by the first ten parameters regardless of forcing, whereas between 74 and 92\% of GPP variance is explained by the first ten parameters. Only the top 50 parameters are shown (of 211) to improve the visualization. Note that parameter rankings differ by variable.}
\label{fig:variance}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{../figs/ET_response.png}
\caption{(a) Global annual average evapotranspiration (ET) in the future climate scenario vs. our control experiment. The shading spans the default ET in the control experiment, $\pm$1 W/m2. The response of ET to future climate with default parameters is +8.8\%. The orange line shows the expected future ET assuming a linear default ET response. 
(b) The top 8 parameters governing global ET in the control experiment.
(c) The top 8 parameters governing ET response to future climate, i.e. the ratio of future ET to control ET.
Parameters governing the change in ET expected in the future tend to differ from the parameters controlling present-day ET.}
\label{fig:et}
\end{figure}

@@

>>>>

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{../figs/variance.png}
\caption{Cumulative fraction of variance explained by the most influential parameters on GPP and canopy evaporation. Approximately 96\% of canopy evaporation variance can be explained by the ten most influential parameters, whereas 30 parameters are required to explain 96\% of GPP variance.}
\label{fig:variance}
\end{figure}

@@

@@

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{../figs/main/NEP_response.png}
\caption{NEP response}
\label{fig:nep}
\end{figure}
